Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic datasets with *mice*

### 2020-08-19 mice_synthesizing/paper.Rmd
Work on intro

An alternative has been offered by @rubin_statistical_disclosure_1993, who, building on the framework of multiple imputation, proposed to release multiple synthetic datasets to the public. Conform this approach, units are sampled randomly and independently from the sampling frame, and their, not observed, values are multiply imputed using a model fitted on the observed data.

>>>>

An alternative has been offered by @rubin_statistical_disclosure_1993, who, building on the framework of multiple imputation, proposed to release multiple synthetic datasets to the public. Conform this approach, all units that are in the population but not in the sample are treated as missing data. These values are imputed by means of conventional multiple imputation approaches, and simple random samples are drawn from the population, and released to the public. In practice, it is not required to impute the complete population, since random samples can be drawn from the sampling frame, so that only these sampled values have to be imputed. The imputed samples generated under this approach are labelled as *fully synthetic datasets*.

A second procedure to creating synthetic datasets has been proposed by @little_statistical_1993, named *partially synthetic datasets*, which yields imputing only those values that are at a high risk of being disclosive. These values can be complete variables that could be compared with publicly available datasets or registers, such as addresses, or it can be certain values that bear a high risk of being disclosive, say, income values above a certain threshold. Similarly to the fully synthetic data approach, multiple datasets containing synthetic values are released to the public, although in this instance, a subset of the data remains constant over the imputations, due to it's non-identifying nature.

-- -- NOT SURE YET: CONTRAST FULLY AND PARTIALLY SYNTHETIC DATA -- --

-- -- SINCE PARTIALLY SYNTHETIC DATA POOLING RULES DO NOT REQUIRE ADJUSTED VARIANCE ESTIMATES -- --

Imputing synthetic values is conceptually similar to the imputations of missing values. That is, conform fully conditional specification, values are drawn iteratively from the posterior predictive distribution of the variable of interest, conditional on all other variables, for each variable separately, where the previously imputed values are taken into account in the imputation model for the variables that are imputed later on. ***ADD MORE INFO FCS***

-- -- CAN WE REGARD THE OBSERVED VALUES AS THE STARTING VALUES FOR THE IMPUTATIONS ? -- --

The R-package `mice` [@mice] implements the fully conditional specification approach for missing data. Since the imputation approaches for missing data and synthetic data do not differ in terms of the imputation process, `mice` can be used for creating synthetic data as well, which will be shown in more detail in the remainder of this paper. Additionally, it will be shown that creating confidence valid [TO DO: FULLY/PARTIALLY] synthetic data can be generated by means of `mice`. However, before introducing `mice` for the creation of synthetic data, the pooling rules for synthetic data will be discussed.

-- -- EXPLAIN MICE -- --

# FULLY/PARTIALLY synthetic data

DISCUSS APPROACH IN MORE DEPTH

# Mice

Discuss mice, predominantly the imputation algorithm in greater depth

# Simulations

## Methods
Boys data - bootstrapped to obtain a population.

## Results
